Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-12 doc/camera-ready/paper.tex
Blai edit

\def\year{2019}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai19}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\usepackage{xcolor}  %Required

@@

\newtheorem{definition}{Definition}
\newtheorem{definitionandtheorem}[definition]{Definition and Theorem}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}
%\newtheorem{example}[definition]{Example}
\newenvironment{example}{\noindent\textbf{Example.}}{\qed}

@@

%PDF Info Is Required (no accents, etc.!):
\pdfinfo{
/Title (Learning Features and Abstract Actions for Computing Generalized Plans)
/Author (Blai Bonet, Guillem Frances, Hector Geffner)}

@@

Finally, problems involving non-deterministic transitions may be
accommodated with a simple fix to the SAT theory.
It would be enough to replace the formula \eqref{eq:bridge1} that
links $D1$ and $D2$ with a formula that says that when $s$ and $t$ are
indistinguishable (i.e.\ $\neg D1(s,t)$), for each action $a$ on $s$,
there is an action $b$ on $t$ whose transitions are indistinguishable
from those of $a$ on $s$. For this, transitions $(s,s')$ in the sample
would need to be tagged with action labels as $(s,a,s')$.

>>>>

\def\year{2019}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai19}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
%\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\usepackage{xcolor}  %Required
\usepackage{xspace}  %Required

@@

\newtheorem{definition}{Definition}
\newtheorem{definitionandtheorem}[definition]{Definition and Theorem}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}
%\newtheorem{example}[definition]{Example}
\newenvironment{example}{\noindent\textbf{Example.}\xspace}{\qed}

@@

%PDF Info Is Required (no accents, etc.!):
\pdfinfo{
/Title (Learning Features and Abstract Actions for Computing Generalized Plans)
/Author (Blai Bonet, Guillem Frances, Hector Geffner)
}

@@

Finally, problems involving non-deterministic transitions may be
accommodated with a simple fix to the SAT theory.
It would be enough to replace the formula \eqref{eq:bridge1} that
links $D1$ and $D2$ with a formula that says that when $s$ and $t$ are
indistinguishable (i.e.\ $\neg D1(s,t)$), for each action $a$ on $s$,
there is an action $b$ on $t$ whose transitions are indistinguishable
from those of $a$ on $s$. To do this, transitions $(s,s')$ in the sample
would need to be tagged with action labels as $(s,a,s')$.
